SylvanSeeds, a seed germination database for temperate deciduous forests

### 2020-08-12 doc/ms/v5_JVS/response-reviewers.Rmd

---
title: "Ref. JVS-R-05435 - Response to reviewers"
author: "Eduardo Fernández Pascual"
date: "12/8/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Editor's comments

> Thanks for your contribution. Two reviewers think your work is valuable but it is necessary you better define the biome (and geographic) scope for inclusion in the database, and also revisit the available data that contributes to your database. You'll see that one reviewer thinks you've missed lots of relevant information. Please address these concerns. If you can do this, the quality of the database will be greatly improved.

Please, find below the response to the comments of the reviewers.

# Referee 1's comments

> This manuscript suggests publication and description of an important data-base on germination features for temperate woodland plants, one of the largest and best documented to date. The data-base has been well prepared, described in detail and two figures summarize geographical extent, variation and mean values.
The amount of data is enormous, and will be an important tool to analyse features of regeneration by seed for forest ecosystems in the world.
The authors restrict their data-base to “Northern Hemisphere” but include on the map biomes and records from Chile, Australia and New Zealand, this should be either corrected in text or in the figure to make it coherent.

We restricted the collection of data to frequent species occurring in vegetation plots of the northern hemisphere. However, the web search for germination data found records of experiments performed with material of those species that had been collected in the southern hemisphere. In other words, the database is for the nemoral flora of the northern hemisphere, but the records come from both that area and other areas where the species can be found. We have added two sentences to the Summary of contents section of the results to clarify this point: *Although the frequent species list was created using only relevés from the northern hemisphere, the web search of germination articles found studies of those species that had been performed in the southern hemisphere. These records are included in the database, and their geographical origin is reported*.

> As to the extent of the biomes it should be stated somewhere that all of these forests undergo frosts (except most of Australia). The ecological description of the biome used might be further be extended with abiotic factors that separate this biome from adjacent ones (frost, drought, etc).

We have included this descriptive sentence in the introduction: *Generally, these forests are characterized by some frost events during the winter while summers are moist and do not suffer drought for any relevant length of time, conditions that favour the dominance of broadleaf deciduous trees*.

> Probably the WWF forest biome source used is not the most relevant here, a map based on the Köppen climate classification or similar would simplify the understanding of the map and also probably better match records to the biome map.

We agree that the Köppen climate classification would probably be more recognisable for many readers. However, we used the WWF classification for a practical reason: it includes a biogeographical regionalization (the ecoregions) which we used to stratify the random sampling of the vegetation plots from which we constructed the frequent species list (please see the methods section for a longer description of the procedure).  We did this to get a homogeneous sampling across the biogeographical regions of the biome. Since this is the regionalization that we used to create the species list, we believe that we should keep the WWF map to delimit the study area. However, to facilitate understanding with the Köppen system, we have included this sentence in the introduction: *Deciduous forests are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers, corresponding with the Cf climate in Köppen's classification (mild temperate, fully humid)*.

> L57: may be You can use “nemoral biome” explaining it as “Temperate Broadleaf and Mixed Forests biome of the northern hemisphere” and avoiding a long and difficult to follow abbreviation? (TBMFNH) or “temperate woodlands” ? This might help to read the text

We have adopted the *nemoral biome* abbreviation in the text, as suggested.

> L193 : may be replace Sown_by_container by Number_per_container

Done.

> L195 : you want to say the “last day” when seeds were counted?

Yes, corrected.

> L195: do you have data on the scarification (=permeabilizing seed coats) method? (physical abrasion, acid treatment, heat shock)?

Sorry, but we did not record this information.

> L201: do you have data on the duration of stratification?

Yes, when this information was reported in the original paper. It is recorded in the column *Stratification_days*.

> L211: why “germinable”? Some of them might have been dead at the beginning? May be “Number_seed” used?

Changed to *Number_seeds*.

> L173: do you maintain a version and backup system for this database in the case updates may come?

The database is maintained in a GitHub repository, which provides a version control system. The repository will be made open when the manuscript is accepted for publication. A website will also be provided, where it will be possible (i) to access the last version of the database; (ii) to be informed about updates; and (iii) to get in contact, to join and contribute data to the database. Please see the last sentences that have been added at the end of the discussion.

> L219: do You think this app can be extended to add data to the data-base?

The app functionality is limited to visualization of the dataset and, as far as we know at this moment, cannot be expanded into a GUI to submit and incorporate data to the database. However, the addition of new data is possible and easy to do using the R code that is behind the app. The website where the app and the database are hosted will provide information on how to contribute data to the database.

# Referee 2's comments

> The idea for a deciduous forest database for seed germination is excellent.  
Some things need to be made more clear than they are now.  The list of included species is relatively short, when one considers the size of the flora of the deciduous forest biome and the amount of work that has been done on seed germination of members of this biome.  Further, species from subalpine coniferous species have been included, and they need to be separated from the deciduous forest species.
Lines 57.  Whose vegetation classification system are you using?   What is the source for the name Temperate Broadleaf and Mixed Forests?

This is the official name of the WWF biome, which we used to sample the vegetation plots that provided the species list (please see the methods, and the response to referee 1). For clarity, we have also added the WWF reference at the first mention of the name in the introduction.

> Line 64. “Baskin, 1995”  is not a good reference to use here.  Why not the Baskin and Baskin 2014 book on seeds?   This reference is not correct on line 64 or in the Literature Cited.   It should be Baskin et al., 1995.  The authors of this paper are Baskin, C. C., Meyer, S.E. and Baskin, J.M.   Also, this paper is not about species that grow in the deciduous forests per se.

We have changed the reference to the Baskin book, as suggested.

> Lines 86-88.  You need to explain to the reader why you have included subalpine coniferous forests of the Cascade Mountains in the same category as deciduous (nemoral) forests of USA, China and Europe.  What vegetation classification systems puts these very different kinds of forests together?

The referee is right that the Cascadia ecoregions do not belong in the TBMF biome. The truth is that these regions were included in the search for practical reasons related to the way the project's workflow was organised, and are unrelated to the deciduous forest biome. Once we had germination records for species from these regions, we had to make the difficult decision of either keeping them (as they are indeed valuable data which might be of interest to the users of the database) or removing them (to keep the homogeneity of the deciduous forest concept).

We have tried to explain this better in the methods section. We have also included a column with the biome variable in the dataset, so the records belonging to species from Cascadia can be identified and separated at any time. Alternatively, if the editor considers it more reasonable, those records could be removed from the dataset and the manuscript.

> Pages 21-500   What is the meaning of all these pages?  These must be references you consulted, but there is no explanation.

These are the supporting materials, please see the Supporting Information section (which is after the bibliography) for a description of the files. We tried to uploaded these files in specific formats (a csv data file and BibTeX bibliographies) but the online submission system forced us to transform them to pdf and appended them at the end of the manuscript. We are sorry by this inconvenience.

> I was shocked when I saw your list of species.  It is not very complete for the deciduous forests, even for eastern North America.  There must be over 100 papers from the Baskin’s work that you have not included.  You should take a look at the Baskin and Baskin (2014) book on seeds.  Look at the list of papers of their own work that they cite.
  I think the idea behind this project is noble and the product will be of great use to people.  However, at this point I think the project is far from being complete.  Also, I think mixing species from the deciduous forests with those from subalpine coniferous forests will create confusion for people in the future who try to use this data base.

We agree that the database is not complete, but we argue that a project of this nature can never be truly complete. As we discuss with the other referee (please also see the new sentences at the end of the discussion) this is a database that intends to be alive, being updated and expanded with future projects, and welcoming collaborators who want to contribute new datasets.

We followed a systematic approach to search for data, with the purpose of prioritising work and maximising its utility for vegetation science. In short, this approach consisted in (i) obtaining a representative number of vegetation plots for the biome from sPlot (https://www.idiv.de/en/splot.html); and (ii) using the plots to produce a list of frequent species (i.e. species that occur in at least 5 % of the plots of a region). Please see the methods for more details.

This systematic approach may leave out relevant information on species of the biome (as the case mentioned by the referee) for three reasons: (1) the species is not recorded in the vegetation databases; (2) the species has been recorded, but it is infrequent; or (3) the species is recorded and frequent and goes into our list, but the relevant germination papers are not found by our web search because the species names is not mentioned in the title or the abstract. While points 1 and 2 are intentionally excluded by our methodology, point 3 would be a failure of the methodology (specifically, a failure of the search string to find a relevant paper).

For this reason, we had applied a protocol to detect the importance of point 3. Incidentally, this protocol used the Baskin book. The protocol consisted in the following: After completing the database, we took the species in our frequent species list for which we had not found relevant papers and searched them in the taxonomical index of the Baskin book. There were 273 species with missing data and mentioned by the Baskins in their index. We took a random sample of 10% of these species and searched the original references in the Baskin book, and found that all of them were either inaccessible (national journals or old conference proceedings not available online) or had no relevant data (i.e. provided no primary germination data that we could retrieve). From this trial, we concluded that our search string had found a reasonable amount of the available information, by comparing it to the best reference possible, the review of the Baskins.

Therefore, the articles mentioned by the referee mostly pertain to species that we intentionally left out of the systematic approach, because of their low representation in vegetation databases. Although of course the approach suggested by the referee is valid, and the information on those works valuable, it is also opportunistic (i.e. it would include references that we are personally aware of, instead of the systematic set of references found by the search based on occurrence in vegetation plots). It is difficult to see where this opportunistic approach would justifiably stop looking for more papers, and consider the database complete.

We believe that the amount of data we provide (primary data extracted from more than 600 references) justifies its utility and the publication of this report as a first building block of a database that will be expanded and maintained. The utility of the dataset is specially justified because, by focusing on frequent species from vegetation databases, it maximises its value for vegetation scientists. As it stands now, it is a good sample of frequent species of the deciduous forest of the northern hemisphere, with a good representation of, for example, many of the dominant tree species.

### 2020-08-12 doc/ms/v5_JVS/ms.Rmd
JVS R1

Seed traits have functional significance in all levels of plant ecology, from population dynamics [@RN3043] to community assembly [@RN2942] and species distributions [@RN2942]. Recent discussions [@RN2352; @RN4655] highlighted the lack of reliable germination databases of wide geographical scope as a major limitation to produce a global synthesis of the seed ecological spectrum. Seed germination is the first major developmental transition in the life of a plant, and it has profound effects on the plant's ecology [@RN2384]. As such, the timing of this transition is controlled by a combination of environmental signals. Amongst these are temperature [@RN2249], diurnal temperature alternation [@RN2217], light [@RN4656] and seed dormancy inductors and relievers [@RN3063]. All of these signals interact to produce a coarse- and fine-scale regulation of germination timing, integrating inputs from both seasonal climatic cycles [@RN3132] and local environmental gradients [@RN2865]. The practical consequence of this is that the response of seeds to, for example, light will depend on other conditions set by the experimenter. This makes it difficult to summarise germination “traits” into a single value in a way comparable to seed mass, specific leaf area or plant height [@RN2923], and may explain the lack of global germination databases. Germination compilations with a biogeographical background, of which the prime example today is the cornerstone book of Baskin and Baskin [-@RN3214], only provide summary information, for instance the interpreted optimal germination temperature instead of the proportion of seeds germinated across a temperature gradient.

To fill this gap, this article presents *SylvanSeeds*, a first global database of raw germination data for an ecologically and biogeographically coherent unit: the Temperate Broadleaf and Mixed Forests biome of the northern hemisphere (*TBMFNH*). Deciduous forests are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers. In the northern hemisphere, they also form a coherent evolutionary and biogeographic unit, sharing a common Tertiary history until they became separated between North America, Asia and Europe [@RN4684]. At the same time, a relatively high number of classic seed biology research groups have worked within the *TBMFNH* areas, e.g. in the USA [@RN1045], the UK [@RN3273], Belgium [@RN656] and Japan [@RN1188]. To create *SylvanSeeds*, a systematic literature search [@RN2401] was applied to a list of frequent species representing the flora of the *TBMFNH*. This article makes the database accessible to the research community. Additionally, the *SylvanSeeds* shiny web app is presented to facilitate the exploration of the data.

@@

A list of species for which to search germination data was created using vegetation relevés (i.e. records of plant species co-occurring in sampling plots) from *sPlot* [@RN4658]. The terrestrial regionalization of the *World Wildlife Fund* [@RN4667] was used to select plots according to their coordinates. To ensure that plots were a representative sample of *TBMFNH* biodiversity, they were chosen from `r MSecoregions` ecoregions distributed throughout the northern hemisphere: 17 ecoregions of the Temperate Broadleaf and Mixed Forests biome (*Appalachian mixed mesophytic forests*, *Atlantic mixed forests*, *Cantabrian mixed forests*, *Caspian Hyrcanian mixed forests*, *Central Korean deciduous forests*, *Dinaric Mountains mixed forests*, *Euxine-Colchic broadleaf forests*, *Hokkaido deciduous forests*, *Manchurian mixed forests*, *Nihonkai evergreen forests*, *Nihonkai montane deciduous forests*, *Pindus Mountains mixed forests*, *Southeastern mixed forests*, *Taiheiyo evergreen forests*, *Taiheiyo montane deciduous forests*, *Western European broadleaf forests*, *Western Great Lakes forests*), plus three neighbouring ecoregions of the Temperate Coniferous Forest biome (*Cascade Mountains leeward forests*, *Central and Southern Cascades forests*, *Eastern Cascades forests*). Although temperate broadleaf and mixed forests also occur in a smaller area of the southern hemisphere, these southern forests form a separate evolutionary and biogeographical unit, not being related by a common history like the northern hemisphere ones [@RN4684].  For this reason, they were not considered. All chosen relevés had been classified as forest plots by *sPlot*, i.e. their plant cover was dominated by tree species. The taxa names were standardized to species level with *The Plant List* [-@RN2321] using the *Taxonstand* package [@RN4660] in *R* version 3.6.2 [@RN2315]. The final vegetation database contained `r MSplots` relevés and `r MStotalspp` standardized species names, considering only seed plants (gymnosperms and angiosperms), and encompassing all forest layers. To obtain the final list of species, only species that were present in at least 5% of the relevés of an ecoregion were kept, rendering a list of `r MSfrequentspp` frequent species. There were two reasons to use this frequency threshold: (i) it made the search achievable with the resources available; and (ii) it filtered out rare species that may not be representative of *TBMFNH*, and which could have been recorded for a variety of reasons (wrong taxonomical identifications, mistakes in plot coordinates, border areas, unnatural areas such as parks, etc.). The result is a list of plant species that occur with relatively high frequency in forest plots of the *TBMFNH*; this includes trees, shrubs and shade-tolerant forbs and grasses, as well as common semi-open species from forest margins, secondary forests, ruderalized forest plots, etc.

@@

The final database contains `r MSrecords` records (germination proportions for a given seed lot of a species, recorded in a set of experimental conditions) from 614 references. The plant materials had been collected across the Temperate Broadleaf and Mixed Forest biome and surrounding areas (**Fig. \@ref(fig:fig1)**), in both hemispheres. The oldest record was from 1920 and the top three contributing countries were the USA (`r MScountries[1, 2]`), the UK (`r MScountries[2, 2]`) and Japan (`r MScountries[3, 2]`). There were `r MSspecies` species represented, from `r MSfamilies` seed plant families. The total estimate of seeds used in the experiments was `r MSseeds`. The range of germination temperatures (weighted average of the daily thermoperiod) went from `r MSminT` to `r MSmaxT` ºC, with `r MSaltY` records of constant temperatures and `r MSaltN` of alternating temperatures. Light was used in `r MSlightY` records, darkness in `r MSlightN` and `r MSlightNA` did not provide information on this parameter. The experiments were performed with unstratified seeds in `r MSstratN` records, and of the rest, the majority (`r MSstratCold`) went through cold stratification. Scarification was applied to `r MSscarY` records.

@@

The database is provided as a *csv* file, comma separated, named **Supporting Information 5** (see online Supporting Information). The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Sown_by_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Germinable* (count of seeds used in the experiment). Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions. Presenting the response variable as a proportion (i.e. number of successes *Germinated*, number of trials *Germinable*) has important benefits for meta-analysis of the database, as proportions can be analysed directly using a GLM, and a variance term does not need to be specified since it is incorporated as part of the analysis [@RN4751].

@@

The database provided in this article, and the web app to visualize it, can have wide applicability in science and beyond. It can extend current trends in global analyses of plant traits at species [@RN3318] and community levels [@RN4664] to seed germination. The ecological determinants of seed germination are also valuable information for species distribution models [@RN3078]. The visualization of the database with the *SylvanSeeds* app can help plant ecologists select experimental treatments that are adequate for their experiments [@RN2999]. Outside of academia, germination data are useful for seed industries [@RN4665], restoration practitioners [@RN2241] and the implementation of regional schemes for seed-based landscape intervention [@RN4666]. The app is accessible to citizens in general who are interested in germinating wild plants. Finally, apart from the database itself, this article can bring two innovations to the seed ecology community, helping to advance the agenda of functional seed ecology [@RN4655]. First, the meta-analysis-inspired methodology used to compile the database can be extended to other biomes and lists of species, contributing to the creation of a global database for ecologically and biogeographically coherent floras. Second, the database and the app can serve as a standard in further efforts to compile and standardize seed germination data.

@@

All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database. The database is provided as Supporting Information. It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/. The code of the app is stored at (note: the GitHub repo is kept private until publication of the manuscript).

>>>>

Seed traits have functional significance in all levels of plant ecology, from population dynamics [@RN3043] to community assembly [@RN2942] and species distributions [@RN2942]. Recent discussions [@RN2352; @RN4655] highlighted the lack of reliable germination databases of wide geographical scope as a major limitation to produce a global synthesis of the seed ecological spectrum. Seed germination is the first major developmental transition in the life of a plant, and it has profound effects on the plant's ecology [@RN2384]. As such, the timing of this transition is controlled by a combination of environmental signals. Amongst these are temperature [@RN2249], diurnal temperature alternation [@RN2217], light [@RN4656] and seed dormancy inductors and relievers [@RN3063]. All these signals interact to produce a coarse- and fine-scale regulation of germination timing, integrating inputs from both seasonal climatic cycles [@RN3132] and local environmental gradients [@RN2865]. The practical consequence of this is that the response of seeds to, for example, light will depend on other conditions set by the experimenter. This makes it difficult to summarise germination “traits” into a single value in a way comparable to seed mass, specific leaf area or plant height [@RN2923], and may explain the lack of global germination databases. Germination compilations with a biogeographical background, of which the prime example today is the cornerstone book of Baskin and Baskin [-@RN3214], only provide summary information, for instance the interpreted optimal germination temperature instead of the proportion of seeds germinated across a temperature gradient.

To fill this gap, this article presents *SylvanSeeds*, a first global database of raw germination data for an ecologically and biogeographically coherent unit: the temperate broadleaf and mixed forests biome [@RN4667] of the northern hemisphere (hereafter shortened to nemoral biome). Nemoral forests are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers, corresponding with the Cf climate in Köppen's classification (mild temperate, fully humid) [@RN4932]. Generally, these forests are characterized by some frost events during the winter while summers are moist and do not suffer drought for any relevant length of time, conditions that favour the dominance of broadleaf deciduous trees [@RN4931]. In the northern hemisphere, they also form a coherent evolutionary and biogeographic unit, sharing a common Tertiary history until they became separated between North America, Asia and Europe [@RN4684]. At the same time, a relatively high number of classic seed biology research groups have worked within the nemoral biome areas, e.g. in the USA [@RN3214], the UK [@RN3273], Belgium [@RN656] and Japan [@RN1188]. To create *SylvanSeeds*, a systematic literature search [@RN2401] was applied to a list of frequent species representing the flora of the nemoral biome. This article makes the database accessible to the research community. Additionally, the *SylvanSeeds* shiny web app is presented to facilitate the exploration of the data.

@@

A list of species for which to search germination data was created using vegetation relevés (i.e. records of plant species co-occurring in sampling plots) from *sPlot* [@RN4658]. The terrestrial regionalization of the *World Wildlife Fund* [@RN4667] was used to select plots according to their coordinates. To ensure that plots were a representative sample of nemoral biome biodiversity, they were chosen from 17 ecoregions of the Temperate Broadleaf and Mixed Forests biome distributed throughout the northern hemisphere: (*Appalachian mixed mesophytic forests*, *Atlantic mixed forests*, *Cantabrian mixed forests*, *Caspian Hyrcanian mixed forests*, *Central Korean deciduous forests*, *Dinaric Mountains mixed forests*, *Euxine-Colchic broadleaf forests*, *Hokkaido deciduous forests*, *Manchurian mixed forests*, *Nihonkai evergreen forests*, *Nihonkai montane deciduous forests*, *Pindus Mountains mixed forests*, *Southeastern mixed forests*, *Taiheiyo evergreen forests*, *Taiheiyo montane deciduous forests*, *Western European broadleaf forests*, *Western Great Lakes forests*). Although temperate broadleaf and mixed forests also occur in a smaller area of the southern hemisphere, these southern forests form a separate evolutionary and biogeographical unit, not being related by a common history like the northern hemisphere ones [@RN4684]. For this reason, they were not considered. For reasons unrelated to the deciduous forest search, three neighbouring ecoregions of the Temperate Coniferous Forest biome (*Cascade Mountains leeward forests*, *Central and Southern Cascades forests*, *Eastern Cascades forests*) were included in the search, and their species were searched for in parallel. For completeness, data from these three regions is also included with the database, but the records from the coniferous forest species are identified so they can be excluded at will (see below).

All chosen relevés had been classified as forest plots by *sPlot*, i.e. their plant cover was dominated by tree species. The taxa names were standardized to species level with *The Plant List* [-@RN2321] using the *Taxonstand* package [@RN4660] in *R* version 3.6.2 [@RN2315]. The final vegetation database contained `r MSplots` relevés and `r MStotalspp` standardized species names, considering only seed plants (gymnosperms and angiosperms), and encompassing all forest layers. To obtain the final list of species, only species that were present in at least 5% of the relevés of an ecoregion were kept, rendering a list of `r MSfrequentspp` frequent species. There were two reasons to use this frequency threshold: (i) it made the search achievable with the resources available; and (ii) it filtered out rare species that may not be representative of the nemoral biome, and which could have been recorded for a variety of reasons (wrong taxonomical identifications, mistakes in plot coordinates, border areas, unnatural areas such as parks, etc.). The result is a list of plant species that occur with relatively high frequency in forest plots of the nemoral biome; this includes trees, shrubs and shade-tolerant forbs and grasses, as well as common semi-open species from forest margins, secondary forests, ruderalized forest plots, etc.

@@

The final database contains `r MSrecords` records (germination proportions for a given seed lot of a species, recorded in a set of experimental conditions) from 614 references. The plant materials had been collected across the Temperate Broadleaf and Mixed Forest biome and surrounding areas (**Fig. \@ref(fig:fig1)**), in both hemispheres. Although the frequent species list was created using only relevés from the northern hemisphere, the web search of germination articles found studies of those species that had been performed in the southern hemisphere. These records are included in the database, and their geographical origin is reported. The oldest record was from 1920 and the top three contributing countries were the USA (`r MScountries[1, 2]`), the UK (`r MScountries[2, 2]`) and Japan (`r MScountries[3, 2]`). There were `r MSspecies` species represented, from `r MSfamilies` seed plant families. The total estimate of seeds used in the experiments was `r MSseeds`. The range of germination temperatures (weighted average of the daily thermoperiod) went from `r MSminT` to `r MSmaxT` ºC, with `r MSaltY` records of constant temperatures and `r MSaltN` of alternating temperatures. Light was used in `r MSlightY` records, darkness in `r MSlightN` and `r MSlightNA` did not provide information on this parameter. The experiments were performed with unstratified seeds in `r MSstratN` records, and of the rest, the majority (`r MSstratCold`) went through cold stratification. Scarification was applied to `r MSscarY` records.

@@

The database is provided as a *csv* file, comma separated, named **Supporting Information 5** (see online Supporting Information). The first row of the file contains the header data, with the following variables: *Biome* (whether the species belongs to temperate broadleaf and mixed foresta [TBMF] or to the temperate coniferous biome [TCF]), *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Number_per_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the last day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Number_seeds* (count of seeds used in the experiment). Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions. Presenting the response variable as a proportion (i.e. number of successes *Germinated*, number of trials *Number_seeds*) has important benefits for meta-analysis of the database, as proportions can be analysed directly using a GLM, and a variance term does not need to be specified since it is incorporated as part of the analysis [@RN4751].

@@

The database provided in this article, and the web app to visualize it, can have wide applicability in science and beyond. It can extend current trends in global analyses of plant traits at species [@RN3318] and community levels [@RN4664] to seed germination. The ecological determinants of seed germination are also valuable information for species distribution models [@RN3078]. The visualization of the database with the *SylvanSeeds* app can help plant ecologists select experimental treatments that are adequate for their experiments [@RN2999]. Outside of academia, germination data are useful for seed industries [@RN4665], restoration practitioners [@RN2241] and the implementation of regional schemes for seed-based landscape intervention [@RN4666]. The app is accessible to citizens in general who are interested in germinating wild plants. Finally, apart from the database itself, this article can bring two innovations to the seed ecology community, helping to advance the agenda of functional seed ecology [@RN4655]. First, the meta-analysis-inspired methodology used to compile the database can be extended to other biomes and lists of species, contributing to the creation of a global database for ecologically and biogeographically coherent floras. Second, the database and the app can serve as a standard in further efforts to compile and standardize seed germination data. The version of the database presented here is a first building block that will be expanded by updating it with more records and integrating it with datasets from other biomes and regions. The website https://efernandezpascual.shinyapps.io/sylvanseeds/ will publish and describe updates. All people interested in contributing to the growth of this germination database are encouraged to contact the corresponding author.

@@

All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database. The database is provided as Supporting Information of this manuscript, but please do visit https://efernandezpascual.shinyapps.io/sylvanseeds/ to check for updates. It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/. The code of the app is stored at (note: the GitHub repo is kept private until publication of the manuscript).
